\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black} 
\usepackage[scale=0.88]{geometry}
\usepackage{enumitem}
\pagenumbering{arabic}
\usepackage{hyperref}



\hypersetup{colorlinks=true, urlcolor=[rgb]{0.15,0.15,0.45}}
\setlist[itemize]{noitemsep,topsep=2pt,leftmargin=1.5em}
\renewcommand*{\namefont}{\fontsize{18}{20}\selectfont}   % default ~28
\renewcommand*{\titlefont}{\fontsize{14}{16}\selectfont}  % default ~14


% ----- personal data -----
\name{Sushant}{Gautam}
\title{PhD Student — Multimodal Understanding}
% \address{Oslo, Norway}
\phone[mobile]{+47 986 72 556}
\email{sushant@simula.no}
\homepage{sushant.info.np}
\social[linkedin]{eSushant}
\social[github]{SushantGautam}
\social[researchgate]{Sushant-Gautam}
\social[googlescholar]{t3Iie8cAAAAJ}

% \extrainfo{Nationality: Nepalese} % optional

\begin{document}
\makecvtitle
\vspace*{-2.0\baselineskip}

%========================
\section{Work Experience}

\cventry{May 2023 -- Present}
        {Ph.D. Student (Full-time)}
        {\href{https://www.simulamet.no/people/sushant}{Simula Metropolitan Center for Digital Engineering (SimulaMet)}}
        {Oslo, Norway}
        {Affiliated with \href{https://www.oslomet.no/en}{Oslo Metropolitan University}}
        {%
        Conducting research on \textbf{multimodal learning for robust and trustworthy vision–language models}; supervising master’s students in AI and medical imaging; representing Simula at the NORA Student Council and organizing academic and outreach events; participating in Simula Academy  outreach programs to inspire and attract master’s students to research.
        }

\cventry{Oct 2024 -- Jul 2025}
        {Ph.D. Enrichment Student for the Turing Enrichment Scheme 2024/25}
        {\href{https://www.turing.ac.uk/people/doctoral-students/sushant-gautam}{The Alan Turing Institute}}
        {London, United Kingdom}
        {}
        {%
          Selected through the Norwegian Artificial Intelligence Research Consortium (NORA); undertook a six-month research stay in London as part of doctoral training; served as Student Representative for the cohort; contributed to discussions that led to the extension of Kvasir-VQA into a multi-task and a multi-complexity benchmark for medical reasoning in gastrointestinal endoscopy; participated in Turing–Roche Co-working sessions, AI-UK 2025 volunteering, and professional development workshops; fostered interdisciplinary collaborations across UK research labs and universities.
        }


\cventry{Oct 2022 -- May 2023}
        {Adjunct Lecturer (Contract-based)}
        {\href{https://tcioe.edu.np/}{Thapathali Campus}, Tribhuvan University}
        {Kathmandu, Nepal}
        {}
        {%
          \begin{itemize}
            \item Lectures and labs for "\textit{A Practical Approach to Deep Learning}" course.
            \item Supervised MS projects related to deep learning.
          \end{itemize}
        }

\cventry{Apr 2019 -- May 2023}
        {Engineering Manager}
        {\href{https://www.nsdevil.com/?lang=en}{North Star Developer's Village}}
        {Lalitpur, Nepal}
        {}
        {%
          \begin{itemize}
            \item ML face verification; pose-based exam cheating prevention; image/audio annotation; ML training platform.
            \item Semantic essay ranking; feedback bot; topic modelling/analysis; ML models exposed via APIs.
          \end{itemize}
        }

\cventry{Oct 2018 -- Mar 2019}
        {AI Intern}
        {\href{https://www.lftechnology.com/}{Leapfrog Technology}}
        {Kathmandu, Nepal}
        {}
        {%
          \begin{itemize}
            \item Predictive models for time-series weather and pollution forecasting (ARIMA and windowing-based).
            \item Model deployment and web-based interactive interface.
          \end{itemize}
        }

\cventry{Jan 2018 -- Sep 2018}
        {Student Research Assistant for UGC Research Grant Project}
        {\href{http://doece.pcampus.edu.np/}{Department of Electronics \& Computer Engineering (DOECE)}}
        {Lalitpur, Nepal}
        {}
        {%
          \begin{itemize}
            \item Assisted Prof.\ Dr.\ Nanda Bikram Adhikari on algorithm/tool research \& implementation.
            \item Sensor data storage with GPS traces \& data mining. Used RNN, RapidMiner, Hadoop, WebSocket, etc.
          \end{itemize}
        }


%========================
\section{Education}


\cventry{May 2023 -- May 2026}
        {Doctor of Philosophy (Ph.D.), at the Faculty of Technology, Art and Design (TKD)}
        {{\href{https://www.oslomet.no/en}{Oslo Metropolitan University (OsloMet)}}}
        {Oslo, Norway}
        {}
        {%
          \textbf{Thesis:} Bridging Multimedia Modalities: Enhanced Multimodal AI Understanding and Intelligent Agents.\\
          \textbf{Coursework:} Topics in AI and ML;  Scientific Research Methods and Data Analysis in Engineering Science; Engineering Science and Ethics; Communicating Scientific Research (Simula Academy); Neural Methods in NLP (University of Oslo).\\
          \textbf{Research Interests:} Multimodal AI; Vision–Language Models; Efficient Model Fine-Tuning; Uncertainty Quantification.
        }

\cventry{Oct 2020 -- Oct 2022}
        {Master's Degree in Informatics \& Intelligent Systems Engineering}
        {\href{https://tcioe.edu.np/}{Thapathali Campus}, Tribhuvan University}
        {Kathmandu, Nepal}
        {}
        {%
          \textit{Full Scholarship for Academic Merit, Top of Class}\\
          \textbf{Relevant coursework:} Natural Language Processing; Computer Vision; Applied Machine Learning; Deep Learning; Computational Intelligence; Information Theory; Information Visualization; Optimization.
        }

\cventry{Oct 2015 -- Oct 2019}
        {Bachelor's Degree in Computer Engineering}
        {\href{https://pcampus.edu.np/}{Pulchowk Campus}, Tribhuvan University}
        {Lalitpur, Nepal}
        {}
        {%
          \textit{Full Scholarship for Academic Merit}\\
          \textbf{Relevant coursework:} Artificial Intelligence; Probability \& Statistics; Data Mining; Big Data; Theory of Computation.
        }
\clearpage
%========================
\section{Technical Capabilities}

\cvitem{Programming}{Python, Android (Java/Kotlin), SQL, Bash, C/C++.}
\cvitem{Libraries and tools}{{ML/DL, data analysis, numerical computing, visualization, web-frameworks, containerization, cloud, and backend-infrastructure ecosystems (including PyTorch, TensorFlow/Keras, NumPy/SciPy, Pandas, Scikit-learn, Matplotlib, OpenCV, Django, FastAPI, HuggingFace, LangChain, vLLM, PEFT/LoRA, Gradio, Streamlit, Git, Docker, Jupyter, etc.).}}
\cvitem{Languages}{English (Fluent), Nepali (Native), Hindi (Advanced), Norwegian (Basic).}

%========================
\section{Academic Projects}

\cvitem{MS Thesis}{%
  \href{https://www.researchgate.net/publication/363857936_AI-based_Soccer_Game_Summarization_From_Video_Highlights_to_Dynamic_Text_Summaries}
  {AI-Based Soccer Game Summarization: From Video Highlights to Dynamic Text Summaries}.\\
  Best thesis in the department (by scores). In collaboration with the Department of Holistic Systems, \textbf{SimulaMet}.
}

\cvitem{MS Project}{%
  \href{https://github.com/SushantGautam/DystViz/}{Deep Learning-based Pose Estimation for Dystonia Score Prediction}.
  In collaboration with \href{https://www.naamii.org.np/}{\textbf{NAAMII}}.
}

\cvitem{Bachelor's Thesis}{%
  \href{https://www.researchgate.net/publication/348620827_Near_Realtime_Assessment_of_Fine_Scale_Spatiotemporal_Weather_Anomalies_and_Pollution_Proxies_Around_Kathmandu_Valley}
  {Assessment of Spatiotemporal Weather and Pollution Proxies with RNN and ARIMA}.\\
  Best Project Award by Department.
}

\cvitem{Bachelor's Project}{%
  \href{https://www.researchgate.net/publication/328043667_MultiLayer_Perceptron_in_Facial_Landmarks_Detection_and_its_Structural_Optimization}
  {Human Facial Landmarks Detection using Multi-Layer Perceptron}.
}

%========================
\section{Selected Publications}
\cvitem{2025}{%
  \href{https://doi.org/10.1007/978-3-032-08009-7_6}
  {Kvasir-VQA-x1: A Multimodal Dataset for Medical Reasoning and Robust MedVQA in Gastrointestinal Endoscopy}. 
  \emph{MICCAI Workshop on Data Engineering in Medical Imaging. LNCS, Springer.}%
}

\cvitem{2024}{%
  \href{https://dl.acm.org/doi/10.1145/3689096.3689458}
  {Kvasir-VQA: A Text-Image Pair GI Tract Dataset}. 
  \emph{VLM4Bio}, ACM Multimedia.%
}

\cvitem{2024}{%
  \href{https://ieeexplore.ieee.org/document/10935951/}
  {SoccerNet-Echoes: A Soccer Game Audio Commentary Dataset}. 
  \emph{IEEE International Symposium on Multimedia}
}

\cvitem{2023}{%
  \href{https://dl.acm.org/doi/10.1145/3577190.3614225}
  {Bridging Multimedia Modalities: Enhanced Multimodal AI Understanding and Intelligent Agents}. 
  \emph{ICMI}, ACM.%
}

\cvitem{2022}{%
  \href{https://dl.acm.org/doi/10.1145/3552463.3557019}
  {Soccer Game Summarization using Audio Commentary, Metadata, and Captions}. 
  \emph{Workshop on User-centric Narrative Summarization of Long Videos (NarSUM)}, ACM Multimedia. (Part of master's thesis work)
}


%========================
\section{Awards \& Certifications}

\cvitem{NAAMII AI Winter School}{%
  \href{https://1nepalschool.naamii.com.np/}{Full scholarship for participation}. Topics: Deep Learning; Computer Vision; Statistics \& Algorithms; Data Science; Optimization.
}
\cvitem{Hult Prize TU Winner (2017)}{%
\href{https://web.archive.org/web/20200923002539/https://glocalkhabar.com/hult-prize-tu-winner-team-aegis-social-entrepreneurship/}{Winning team “AEGIS”}. Presented a sustainable idea to empower refugees in Nepal using an e-commerce platform; presented at Hult Business School, Dubai.
}
\cvitem{Mentor}{Global Venture Bootcamp, Asian Development Bank, Philippines — enhancing social ventures with emerging technologies.}
\cvitem{Participant}{IEEE AI \& Big Data Workshop 2018; led multiple IEEE Student Chapter activities on campus.}
\cvitem{Participant}{UNICEF 1000 Golden Hours Code Camp (2017) — Best Prototype Award for mobile app idea.}

%========================
\section{References}

\cvitem{Prof.\ Pål Halvorsen}{Chief Research Scientist, SimulaMet; Professor, OsloMet; Adjunct Professor, UiO, Norway \\
\href{mailto:paalh@simula.uio.no}{paalh@simula.uio.no} / \href{mailto:paalh@ifi.uio.no}{paalh@ifi.uio.no}; +47 97080007.}

\cvitem{Dr.\ Michael Riegler}{Head of AI, Simula Research Laboratory, Norway \\
\href{mailto:michael@simula.no}{michael@simula.no}; +47 401 06 386.}

\cvitem{Dr.\ Vajira Thambawita}{Senior Research Scientist, Department of Holistic Systems (HOST), SimulaMet, Norway. \\
\href{mailto:vajira@simula.no}{vajira@simula.no}; +47 908 06 683.}


%========================
\vfill
\begin{flushright}
{\footnotesize Compiled: \today \quad|\quad Updated: October 1, 2025 \quad|\quad Check \href{https://sushant.info.np/resume}{sushant.info.np/resume} for updates.}
\end{flushright}

\end{document}