\color{black}

\newgeometry{right=1.5cm, top=1.5cm}
\onehalfspacing
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\href{https://www.jobbnorge.no/en/available-jobs/job/237204/phd-research-fellow-in-deep-learning-for-images}{\textbf{Advertisement Link}}

\textbf{WORK IN PROGRESS...}


Dear Hiring Manager,

I am writing to express my interest in the PhD Research Fellow in Deep Learning for Images position that is currently available at the University of Oslo. I am confident that my educational background in Informatics and Intelligent Systems Engineering, as well as my technical capabilities and work experiences, make me an ideal candidate for this opportunity.

Relevant graduate courses in Computer Vision, Applied ML, Deep Learning for Visual Analytics, Information Theory, Information Visualization and Advanced Optimization, and NLP including an in-depth study of attention mechanism in Transformers  have provided me with a solid foundation in deep learning, mathematics, linear algebra, and statistics. Additionally, I have experience with Python programming, as well as knowledge of PyTorch and TensorFlow/Keras, which are critical for the research challenges that the position is addressing.

In my current role as an Adjunct Lecturer at Tribhuvan University, I am responsible for lecturing and lab work for a Practical Approach to Deep Learning course and I am also supervising two MS projects related to deep learning with Computer Vision. One of them is related to tracking spermatozoa from clinical videos and another is related to anomaly detection in clinical images.
Additionally, my experience as a software project manager at UBL R\&D Center and as an AI intern at Leapfrog Technology has provided me with experience in developing and implementing deep learning solutions for a variety of applications not just limited to computer vision, mostly related to the education domain like an online exam proctoring, student's behaviour monitoring through webcam and student's essay ranking.

I faced the problem with limited training data, and explainability while I worked on my MS project related to pose-based medical score prediction for dystonia. I also have suffered in  proper capturing of the  context and dependencies while training models. From my experiences around ML/DL applications with a roller coaster of success and failures, I have a made strong zeal to work on research challenges with Dl. I am also excited about the opportunity to work with real image data sets collected by the Institute of Marine Research for the sustainable management of resources in marine ecosystems.

In addition to my technical qualifications, I possess good analytical skills and dedication to working with important applications. As of now, I provide hands-on supervision (more interactive) to my MS students. 

I worked with Soccer pipelines for my MS thesis which was a mixture of various components. Fixing periodic bugs and quickly learning all those new things to inter\-operate them was a daily routine.
 I was fortunate to work in a very collaborative environment on a bigger project at SimulaMet where many research groups were working together at the same time. I got a chance to work independently and supervised through strict weekly meetings and also had to  share my progress and findings with multidisciplinary teams, and give as well as receive constructive scientific criticism about the progress. I just had a few days to respond to feedback and it encouraged me to work with top most dedication so that I can do something new and share it with my peers before the next meeting. 



I am eager to be part of a network of young researchers in deep learning at the Visual Intelligence Graduate School and to contribute to the centre's seminars. I am also excited about the opportunity to collaborate with user partners within Visual Intelligence and to seek collaboration between the research partners within the centre.  I want to be involved in cutting-edge research and always be in sync with the development and progress in the domain of deep learning and computer vision.

I would like to thank you for considering my application. I look forward to the opportunity to discuss my qualifications further.

Sincerely,

Sushant Gautam
